Human-level control through deep reinforcement learning

### 2017-12-24 article/article.tex
[Article] Action space, normalized performance, preprocessing

Since we are handling visual features, we used screen frames as environment state representations. Each frame is a (210 x 160) color image sampled at
a frequency of 60 Hz. We denote the environment state at current step $t$ by $s_t$. The agent gathers experience by incorporating new experience samples
to its history. An experience is a tuple $e_t = (s_t, a_t, r_t, s_{t+1})$ appended to the experience history immediately after being generated.
To prevent the agent from forgetting the history and increase the bias towards most recent experience samples, we have recourse on the experience
replay algorithm. One can straightforwardly implement it as a uniform sampling algorithm that returns random experience samples at each step.
We compared this technique to a more efficient approach called prioritized experience replay \citep{DBLP:journals/corr/SchaulQAS15}.

  \todo{Antoine suite}

It has been shown that DQN has an ability to learn by acquiring experience generated from policies other than its own.

@@

  \todo{pour Robin}

  \todo{Citer ALE} \citep{bellemare13arcade}

>>>>

Since we are handling visual features, we used screen frames as environment state representations. Each frame is a (210 x 160) color image sampled at
a frequency of 60 Hz. We denote the environment state at current step $t$ by $s_t$. The agent gathers experience by incorporating new experience samples
to its history. An experience is a tuple $e_t = (s_t, a_t, r_t, s_{t+1})$ appended to the experience history immediately after being generated.
To prevent the agent from forgetting the history and increase the bias towards most recent experience samples, we have recourse to the experience
replay algorithm. One can straightforwardly implement it as a uniform sampling algorithm that returns random experience samples at each step.
We compared this technique to a more efficient approach called prioritized experience replay \citep{DBLP:journals/corr/SchaulQAS15}.
To emphasize the importance of the memory replay mechanism, we compared the results obtained using prioritized experience replay, regular
experience replay, and no experience replay.

Every 4 steps of the Q-learning, the agent builds a minibatch from its memory (either one of the three mechanisms we just mentioned):
this minibatch is used by the DQN to process one step of stochastic gradient descent. In this way the values of Q are estimated iteratively and
refined over time. The deep neural network incorporates minimal prior knowledge about the environment: the only assumption lies in the number of 
outputs in the last hidden layer, which has been set as the number of actions. In every Atari game, the action space is discrete and finite: this allows
us to determine the output shape of the neural network depending on the game itself. The number of actions made available by the environment
cannot be inferred by the DQN during training phase.

Also we compared DQN, as well as other state-of-the-art deep reinforcement learning architectures, to simpler reinforcement learning techniques (including
random action selection) using a normalized performance metric. The latter is formalized as below:
\[
    P = 100 \times (score - RAS) / (HS - RAS)
\]
where P designates the normalized performance, RAS the random action selection score, and HS the human score obtained in average by our
Space Invaders professional gamer \textbf{Stanislas Gueniffey}. By normalizing in this manner, the random action selection score RAS results in
a normalized performance of 0\% and the human score results in a normalized performance of 100\%.

Finally it has been pointed out by the original DQN conceptors that DQN has an ability to learn by acquiring experience generated from policies
other than its own. \todo{On peut en faire qqch pas vrai ?}

\todo{introduce DDDQN}

@@

Our source code is available at \url{https://github.com/RobinPetit/Learning-Chaos}

We developed our models with the support of the Arcade Learning Environment \citep{bellemare13arcade}. This gives the opportunity to either
retrieve the environment state as a raw image (for deep reinforcement learning research) or as a state of the RAM (for classic reinforcement learning
applications). Because of the very high dimensionality of raw images, we applied some preprocessing steps on them. These steps are also aimed at 
removing some artifacts produced by the Atari architecture. More specifically, the flickering effect implies that some game sprites only appear
in one out of two frames. An easy solution consists in taking the pixelwise maximum value between the current frame and the previous frame.
Then the sample size has been reduced by a factor of three by mapping RBG values to the pixel luminance, using the following formula:
\[
    luminance = 0.299 \times R + 0.587 \times G + 0.114 \times B
\]
After mapping the three color channels to a unique channel, the number of pixels has also been reduced. Each input image as been rescaled to a
$84 \times 84$ pixel grid.

\todo{Suite: CNN architecture}
